Spike-and-Slab Generalized Additive Models and Scalable Algorithms for High-Dimensional Data

### 2022-02-18 Manuscript/00-main.Rmd

\newpage

```{r, results = "asis"}
sim_gaus_tab$mgcv[4] <- "-"
sim_gaus_tab$mgcv[5] <- "-"
sim_gaus_tab %>% 
  mutate(p = as.integer(p)) %>% 
  rename(
    "P" = p,
    "BHAM-IWLS" = bglm_spline_de,
    "BHAM-CD" = blasso_spline,
    "COSSO" = cosso,
    "Adaptive COSSO" = acosso,
    "SB-GAM" = SB_GAM
  ) %>% 
  xtable(
    align = "cccccccc",
    caption = "The average and standard deviation of the out-of-sample $R^2$ measure for Gaussian outcomes over 50 iterations. The models of comparison include the proposed Bayesian hierarchical additive model (BHAM) fitted with Iterative Weighted Least Square (BHAM-IWLS) and Coordinate Descent (BHAM-CD) algorithms, component selection and smoothing operator (COSSO), adaptive COSSO, mgcv and sparse Bayesian generalized additive model (SB-GAM). mgcv doesn't provide estimation whe number of parameters exceeds sample size i.e. p = 100, 200.",
    label = "tab:gaus") %>% 
  print(comment = FALSE, include.rownames = FALSE)
  # flextable(
  #   # col_keys = c("P", "BHAM-IWLS", "BHAM-CD", "COSSO", "Adaptive COSSO", "mgcv", "SB-GAM")
  # ) %>% 
  # flextable::autofit() %>% 
  # flextable::set_caption(caption = "The average and standard deviation of the out-of-sample $R^2$ measures for Gaussian outcomes over 50 iterations. The models of comparison include the proposed Bayesian hierarchical additive model (BHAM) fitted with Iterative Weighted Least Square (BHAM-IWLS) and Coordinate Descent (BHAM-CD) algorithms, component selection and smoothing operator (COSSO), adaptive COSSO, mgcv and sparse Bayesian generalized additive model (SB-GAM). \\label{tab:gaus}")
```

@@

\newpage
<!-- \begin{landscape} -->
```{r results = "asis"}
sim_tim_tab %>% 
  select(dist, p, `BHAM-IWLS`,`BHAM-CD`, cosso, acosso, mgcv, `SB-GAM`) %>% 
  rename(Distribution = dist,
         P = p,
         COSSO = cosso,
         `Adaptive COSSO` = acosso) %>% 
   xtable(
    caption = "The average and standard deviation of computation time in seconds, including cross-validation and final model fitting, over 50 iterations. The models of comparison include the proposed Bayesian hierarchical additive model (BHAM) fitted with Iterative Weighted Least Square (BHAM-IWLS) and Coordinate Descent (BHAM-CD) algorithms, component selection and smoothing operator (COSSO), adaptive COSSO, mgcv and sparse Bayesian generalized additive model (SB-GAM). mgcv doesn't provide estimation whe number of parameters exceeds sample size i.e. p = 100, 200.",
    label = "tab:time_sim",
    booktabs = TRUE
  ) %>% 
  print(comment = FALSE, include.rownames = FALSE,
       floating.environment = "sidewaystable",# caption.placement = "top"
       table.placement = "!h"
        )

  # flextable::flextable() %>% 
    # merge_v(j = 1) %>% 
  # width(j=1, width=1) %>% 
  # autofit() %>%
  # flextable::set_caption(caption = "The average and standard deviation of computation time in seconds, including cross-validation and final model fitting, over 50 iterations. The models of comparison include the proposed Bayesian hierarchical additive model (BHAM) fitted with Iterative Weighted Least Square (BHAM-IWLS) and Coordinate Descent (BHAM-CD) algorithms, component selection and smoothing operator (COSSO), adaptive COSSO, mgcv and sparse Bayesian generalized additive model (SB-GAM). mgcv doesn't provide estimation whe number of parameters exceeds sample size i.e. p = 100, 200.\\label{tab:time_sim}")
```
<!-- \end{landscape} -->
\newpage

>>>>

\clearpage

```{r, results = "asis"}
sim_gaus_tab$mgcv[4] <- "-"
sim_gaus_tab$mgcv[5] <- "-"
sim_gaus_tab %>% 
  mutate(p = as.integer(p)) %>% 
  rename(
    "P" = p,
    "BHAM-IWLS" = bglm_spline_de,
    "BHAM-CD" = blasso_spline,
    "COSSO" = cosso,
    "Adaptive COSSO" = acosso,
    "SB-GAM" = SB_GAM
  ) %>% 
  xtable(
    align = "cccccccc",
    caption = "The average and standard deviation of the out-of-sample $R^2$ measure for Gaussian outcomes over 50 iterations. The models of comparison include the proposed Bayesian hierarchical additive model (BHAM) fitted with Iterative Weighted Least Square (BHAM-IWLS) and Coordinate Descent (BHAM-CD) algorithms, component selection and smoothing operator (COSSO), adaptive COSSO, mgcv and sparse Bayesian generalized additive model (SB-GAM). mgcv doesn't provide estimation whe number of parameters exceeds sample size i.e. p = 100, 200.",
    label = "tab:gaus") %>% 
  print(comment = FALSE, include.rownames = FALSE)
  # flextable(
  #   # col_keys = c("P", "BHAM-IWLS", "BHAM-CD", "COSSO", "Adaptive COSSO", "mgcv", "SB-GAM")
  # ) %>% 
  # flextable::autofit() %>% 
  # flextable::set_caption(caption = "The average and standard deviation of the out-of-sample $R^2$ measures for Gaussian outcomes over 50 iterations. The models of comparison include the proposed Bayesian hierarchical additive model (BHAM) fitted with Iterative Weighted Least Square (BHAM-IWLS) and Coordinate Descent (BHAM-CD) algorithms, component selection and smoothing operator (COSSO), adaptive COSSO, mgcv and sparse Bayesian generalized additive model (SB-GAM). \\label{tab:gaus}")
```
\clearpage

@@

\clearpage
<!-- \begin{landscape} -->
```{r results = "asis"}
sim_tim_tab %>% 
  select(dist, p, `BHAM-IWLS`,`BHAM-CD`, cosso, acosso, mgcv, `SB-GAM`) %>% 
  rename(Distribution = dist,
         P = p,
         COSSO = cosso,
         `Adaptive COSSO` = acosso) %>% 
   xtable(
    caption = "The average and standard deviation of computation time in seconds, including cross-validation and final model fitting, over 50 iterations. The models of comparison include the proposed Bayesian hierarchical additive model (BHAM) fitted with Iterative Weighted Least Square (BHAM-IWLS) and Coordinate Descent (BHAM-CD) algorithms, component selection and smoothing operator (COSSO), adaptive COSSO, mgcv and sparse Bayesian generalized additive model (SB-GAM). mgcv doesn't provide estimation whe number of parameters exceeds sample size i.e. p = 100, 200.",
    label = "tab:time_sim",
    booktabs = TRUE
  ) %>% 
  print(comment = FALSE, include.rownames = FALSE,
       floating.environment = "sidewaystable",# caption.placement = "top"
       table.placement = "!h"
        )

  # flextable::flextable() %>% 
    # merge_v(j = 1) %>% 
  # width(j=1, width=1) %>% 
  # autofit() %>%
  # flextable::set_caption(caption = "The average and standard deviation of computation time in seconds, including cross-validation and final model fitting, over 50 iterations. The models of comparison include the proposed Bayesian hierarchical additive model (BHAM) fitted with Iterative Weighted Least Square (BHAM-IWLS) and Coordinate Descent (BHAM-CD) algorithms, component selection and smoothing operator (COSSO), adaptive COSSO, mgcv and sparse Bayesian generalized additive model (SB-GAM). mgcv doesn't provide estimation whe number of parameters exceeds sample size i.e. p = 100, 200.\\label{tab:time_sim}")
```
<!-- \end{landscape} -->
\clearpage
